Adversarial Variational Optimization of\\ Non-Differentiable Simulators

### 2018-02-01 icml/avo.tex
save

% \subsection{Benchmarks}
%
% \glnote{Compare against ABC and others.}
% \glnote{Sections 6.1 and 6.4 of Bernton.}

@@

In this note, we develop a likelihood-free inference algorithm for
non-differentiable, implicit generative models. The algorithm combines
adversarial training  with variational optimization to minimize variational
upper bounds  on the otherwise non-differentiable adversarial objectives. The
AVO algorithm enables empirical Bayes through variational inference in the
likelihood-free setting. This approach does not incur the inefficiencies of an
ABC-like rejection sampler. When the model is well-specified, the AVO algorithm
provides point estimates for
the generative model, which asymptotically corresponds to the data generating
parameters. The algorithm works on continuous or discrete data.

Preliminary results on toy problems with discrete and continuous data validate
the proposed method. While the obtained results are encouraging, the complete
validation of the method remains to be carried out in real conditions on a full
fledged scientific simulator -- which we plan to achieve for a next version of
this work \glnote{to update}. In terms of method, several components need further investigation.
First, we need to better study the interplay between the entropic regularization and the
adversarial objectives. Second, we should better understand the dynamics of the
optimization procedure, in particular when combined with momentum-based
optimizers like Adam. Third, we need to consider whether less noisy estimates of
the gradients $\nabla_\bfpsi U_g$ can be computed.

>>>>

\subsection{Benchmarks}

\glnote{Compare against ABC and others.}
\glnote{Sections 6.1 and 6.4 of Bernton.}

@@

In this work, we develop a likelihood-free inference algorithm for
non-differentiable, implicit generative models. The algorithm combines
adversarial training  with variational optimization to minimize variational
upper bounds  on the otherwise non-differentiable adversarial objectives. The
AVO algorithm enables empirical Bayes through variational inference in the
likelihood-free setting. This approach does not incur the inefficiencies of an
ABC-like rejection sampler. When the model is well-specified, the AVO algorithm
provides point estimates for
the generative model, which asymptotically corresponds to the data generating
parameters. The algorithm works on continuous or discrete data.

\glnote{to update}
Preliminary results on toy problems with discrete and continuous data validate
the proposed method. While the obtained results are encouraging, the complete
validation of the method remains to be carried out in real conditions on a full
fledged scientific simulator -- which we plan to achieve for a next version of
this work. In terms of method, several components need further investigation.
First, we need to better study the interplay between the entropic regularization and the
adversarial objectives. Second, we should better understand the dynamics of the
optimization procedure, in particular when combined with momentum-based
optimizers like Adam. Third, we need to consider whether less noisy estimates of
the gradients $\nabla_\bfpsi U_g$ can be computed.
